---
title: "Exploratory Data Analysis"
author: "STOR 320.(01) Group 6 (Ex: STOR 320.01 Group 12)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# Import Data Below
# read_csv()
dt = read_csv('Placement_Data_Full_Class.csv')
```

# Creator: FIRSTNAME LASTNAME

### Q1: WRITE_QUESTION_HERE

```{r}
#
```

### Q2: WRITE_QUESTION_HERE

```{r}
#
```

# Interpreter: Yunzhou Liu

### Q1: Is there a correlation between employability test and salary?

```{r}
#
# Need to first drop the NAs
# Test for correlation
wo.NA = dt %>% filter(!is.na(etest_p) & !is.na(salary))
cor(wo.NA$etest_p, wo.NA$salary)
wo.NA %>% ggplot(mapping=aes(x=etest_p, y=salary))+geom_point()+geom_smooth()
```

The `cor` output gives us the correlation between `employability test` and `salary`, which is `r cor(wo.NA$etest_p, wo.NA$salary)`. And thus we can see that there is a **weak positive correlation** between `employability test` and `salary`. 

### Q2: Are there any significant differences of salaries between different fields of undergraduate research?

```{r}
wo.NA2 = dt %>% filter(!is.na(degree_t) & !is.na(salary))
wo.NA2 %>% ggplot(mapping=aes(x=degree_t, y=salary))+geom_boxplot()+geom_point(data=wo.NA2 %>% group_by(degree_t) %>% summarise(deg.mean = mean(salary)) %>% ungroup(), mapping=aes(x=degree_t, y=deg.mean, color='red'))
TukeyHSD(aov(salary~degree_t, data=wo.NA2))
```

From the boxplot above, we can assume that there is not a significant differences of salaries between different fields of undergraduate research. 
And we propose our Null and Alternative Hypotheses: 

- Null Hypothesis $H_{0, i, j}$: There is **no difference** in mean between two groups of different field of undergraduate research for any two groups ${i, j}$
- Alternative Hypothesis $H_{A, i, j}$: There is **at least one group** with mean significantly different from another group. 

We can see from the Tukey HSD test above that all of these adjusted p-values are larger than 5%, which means that we reject our alternative hypothesis, and there **isn't a significant difference in salary between different field of study**.

# Orator: Camryn Blawas

### Q1: Do secondary education percentage and higher secondary education percentage have an effect on job placement ?

```{r}
PlacementData = read.csv("PlacementData.csv")
SE_Data = select(PlacementData, "SE_Grade", "JobStatus")
SE_Data = mutate(SE_Data, Year = ifelse(is.na(SE_Grade), NA, "SE_Grade"), Grade = SE_Grade)
SE_Data1 = select(SE_Data, "Grade", "JobStatus", "Year")
HSE_Data = select(PlacementData, "HSE_Grade", "JobStatus")
HSE_Data = mutate(HSE_Data, Year = ifelse(is.na(HSE_Grade), NA, "HSE_Grade"), Grade = HSE_Grade)
HSE_Data1 = select(HSE_Data, "Grade", "JobStatus", "Year")
All_Grades = rbind(SE_Data1, HSE_Data1)
ggplot(All_Grades,aes(x=JobStatus, y=Grade, fill=Year)) +
  geom_boxplot() +
  stat_boxplot(geom = 'errorbar')
```
This graph leads us to believe there is a relationship between secondary education grades and job placement. More statistical analyses will be necessary to positively determine this relationship. 

### Q2: What is the effect of undergraduate degree type and MBA specialization on salary?

```{r}
PlacementData = read.csv("PlacementData.csv")
SciTechUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
SciTechUG_MktFinMBA = mutate(SciTechUG_MktFinMBA, Special = ifelse(UG_Specialization == "Sci&Tech" & MBA_Specialization == "Mkt&Fin","SciTechUG_MktFinMBA", NA))
SciTechUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
SciTechUG_MktHRMBA = mutate(SciTechUG_MktHRMBA, Special = ifelse(UG_Specialization == "Sci&Tech" & MBA_Specialization == "Mkt&HR","SciTechUG_MktHRMBA", NA))
CommMgmtUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
CommMgmtUG_MktFinMBA = mutate(CommMgmtUG_MktFinMBA, Special = ifelse(UG_Specialization == "Comm&Mgmt" & MBA_Specialization == "Mkt&Fin","CommMgmtUG_MktFinMBA", NA))
CommMgmtUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
CommMgmtUG_MktHRMBA = mutate(CommMgmtUG_MktHRMBA, Special = ifelse(UG_Specialization == "Comm&Mgmt" & MBA_Specialization == "Mkt&HR","CommMgmtUG_MktHRMBA", NA))
OtherUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
OtherUG_MktFinMBA = mutate(OtherUG_MktFinMBA, Special = ifelse(UG_Specialization == "Others" & MBA_Specialization == "Mkt&Fin","OtherUG_MktFinMBA", NA))
OtherUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
OtherUG_MktHRMBA = mutate(CommMgmtUG_MktHRMBA, Special = ifelse(UG_Specialization == "Others" & MBA_Specialization == "Mkt&HR","OtherUG_MktHRMBA", NA))
Q8Data= rbind(SciTechUG_MktFinMBA, SciTechUG_MktHRMBA, CommMgmtUG_MktFinMBA, CommMgmtUG_MktHRMBA, OtherUG_MktFinMBA, OtherUG_MktHRMBA)
Q8Data1 = na.omit(Q8Data)
ggplot(Q8Data1, aes(x=Special, y=Salary))+
  geom_boxplot() +
  stat_boxplot(geom = 'errorbar') +
  coord_flip()
```
This graph leads us to believe that there is no significant effect of undergraduate degree type and MBA specialization on salary. However, more statistical analyses will be needed to determine if this is true. 


# Deliverer: FIRSTNAME LASTNAME

### Q1: WRITE_QUESTION_HERE

```{r}
#
```

### Q2: WRITE_QUESTION_HERE

```{r}
#
```

# Follow-up Questions

### New Questions Based Off Initial Investigation

- Q1: What is the relationship between MBA specialization and job placement?
- Q2: What determines if individuals are placed?
- Q3: Can we predict the salary of those who are placed?
- Q4: How is the undergraduate experience (degree percentage & field of study) relate to the employability test score? 

### Investigation of Follow-up Questions

GIVE WHAT 2 QUESTIONS YOU ATTEMPTED TO INVESTIGATE FURTHER IN COMPLETE SENTENCES (*Example:* Our group decided to investigate Q2 and Q4 in further detail.)

SHOW AT LEAST 2 TABLES OR FIGURES BELOW THAT EXPLORE ANSWERS FOR THE QUESTIONS YOU ARE INVESTIGATING FURTHER.

Our group decided to investigate Q1 and Q4 in further detail. 

```{r}
# Q1
PlacementData = read.csv("PlacementData.csv")
attach(PlacementData)
ggplot(PlacementData, aes(x=MBA_Specialization, fill=JobStatus))+
  geom_bar()
table <- table(JobStatus, MBA_Specialization) 
table 
prop.table(table)
chisq.test(table)
```

From the plot given, we can compare MBA specialization with job placement. The results of the chi-squared test indicate that we can reject the null hypothesis (that MBA specialization does not result in any effect on job placement) due to a statistically significant p-value of 0.0004202 (<0.05).  

```{r}
# Q4
ggplot(data=dt, mapping=aes(x=degree_p, y=etest_p, color=degree_t))+geom_point()+geom_smooth()

without.degree_t = lm(etest_p~degree_p, data=dt)
with.degree_t = lm(etest_p~degree_p+degree_t, data=dt)
smr.with.degree_t = summary(with.degree_t)
anova.degree_t = anova(without.degree_t, with.degree_t)
smr.with.degree_t
anova.degree_t[2, 6]
```

From the plot above, we can see that `degree percentage` might have a weak positive relationship with `employability test` score, while the `field of research` does not have a large impact on the overall relationship between `degree_p` and `etest_p`. 
Hence, we can first conclude that `degree percentage` might be a significant factor for predicting `employability test` score, but different `field of study` might not affect the result of prediction from `degree percentage`. 

This can be proven by the model summary and anova table, where we first see that the model with both `degree_p` and `degree_t` included gives a p-value of `r smr.with.degree_t$coefficients[2, 4]` for `degree_p` , which is significant at 5% level. 
But both levels of `degree_t` are not significant even at 10% level, indicating that `degree_t` might not be a good predictor for `etest_p`. 

We then perform nested test to check if adding `degree_t` would explain more variability of `etest_p`, and the p-value provided is not significant (`r anova.degree_t[2, 6]`) at 5% level. Hence, we can conclude that , `field of research` does not explain much extra variability for `etest_p`. 

# Summary

GIVE A 2 PARAGRAPH SUMMARY. 

PARAGRAPH 1 SHOULD DESCRIBE WHAT YOU LEARNED ABOUT YOUR DATA FROM INVESTIGATING THE INITIAL QUESTIONS. DID YOU FIND ANYTHING UNUSUAL IN YOUR DATA? DID ANYTHING SURPRISE YOU? WHICH OF THE INITIAL QUESTIONS WERE HELPFUL IN LEADING YOU TO MORE QUESTIONS?
- Something that suprised me was the effect of secondary education grades on job placement, and the lack of effect of both degree types on salary.  

PARAGRAPH 2 SHOULD SUMMARIZE WHAT YOU LEARNED FROM INVESTIGATING THE FOLLOW-UP QUESTIONS. WHY ARE THESE FOLLOW-UP QUESTIONS INTERESTING FOR INVESTIGATION? DESCRIBE THE TABLES/FIGURES YOU USED TO EXPLORE ANSWERS TO THESE FOLLOW-UP QUESTIONS? WHAT DID YOU LEARN FROM THE TABLES/FIGURES REGARDING THE FOLLOW-UP QUESTIONS YOU PROPOSED?
- From question 1, we decided to investigate the relationship between MBA specialization and job placement because we wanted to see if a certain degree type was more likely to result in an employment opportunity. The figure and table used in this demonstrated that we can reject the null hypothesis (that MBA specialization does not result in any effect on job placement, due to a statistically signficant p-value. This would lead us to investigate further into the relationships between MBA specialization and job placement. 














