---
title: "Yunzhou - Exploratory Data Analysis"
author: "Yunzhou Liu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---
```{r include=FALSE}
library(readr)
library(tidyverse)
```

# Import Dataset

```{r message=FALSE}
dt = read_csv('Placement_Data_Full_Class.csv')
```

### Question 1: Is there a correlation between employability test and salary?

```{r}
# Need to first drop the NAs
# Test for correlation
wo.NA = dt %>% filter(!is.na(etest_p) & !is.na(salary))
cor(wo.NA$etest_p, wo.NA$salary)
wo.NA %>% ggplot(mapping=aes(x=etest_p, y=salary))+geom_point()+geom_smooth()
```

From the `cor` function output, we can see that there is a weak positive correlation between `employability test` and `salary`. 

### Question 2: Are there any significant differences of salaries between different fields of undergraduate research?

```{r}
wo.NA2 = dt %>% filter(!is.na(degree_t) & !is.na(salary))
wo.NA2 %>% ggplot(mapping=aes(x=degree_t, y=salary))+geom_boxplot()+geom_point(data=wo.NA2 %>% group_by(degree_t) %>% summarise(deg.mean = mean(salary)) %>% ungroup(), mapping=aes(x=degree_t, y=deg.mean, color='red'))
TukeyHSD(aov(salary~degree_t, data=wo.NA2))
```

From the boxplot above, we can assume that there is not a significant differences of salaries between different fields of undergraduate research. 
And we propose our Null and Alternative Hypotheses: 

- Null Hypothesis $H_{0, i, j}$: There is **no difference** in mean between two groups of different field of undergraduate research for any two groups ${i, j}$
- Alternative Hypothesis $H_{A, i, j}$: There is **at least one group** with mean significantly different from another group. 

We can see from the Tukey HSD test above that all of these adjusted p-values are larger than 5%, which means that we reject our alternative hypothesis, and there **isn't a significant difference in salary between different field of study**.
